The Exoplanet Orbit Database \textsc{II}: 2014 updates

### 2014-03-20 draft/ms.tex
Add note on mass cut criterion of EOD.

The rest of the selection criteria for the EOD remain unchanged. We
still require the planets to be smaller than 24 \mjup\ and to have
robust detections and well-determined orbits (though these are not
strictly quantitative; see Section~2 of \citealt{Wright2011}). When
new evidence comes to light and we are no longer confident about the
planet, we remove it from EOD, even if the evidence is not peer
reviewed.

>>>>

The rest of the selection criteria for the EOD remain unchanged. We
still require the planets to be smaller than (ZZZ change to mass
ratio) 24 \mjup\ and to have robust detections and well-determined
orbits (though these are not strictly quantitative; see Section~2 of
\citealt{Wright2011}). When new evidence comes to light and we are no
longer confident about the planet, we remove it from EOD, even if the
evidence is not peer reviewed.
